---
title: "STAT/MATH 495: Problem Set 07"
author: "Wayne Maumbe"
date: "2017-10-24"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(broom)
library(knitr)
library(ROCR)

train <- read_csv("data/cs-training.csv") %>% 
  rename(Id = X1)
test <- read_csv("data/cs-test.csv") %>% 
  rename(Id = X1)
submission <- read_csv("data/sampleEntry.csv")
drawtrain<-train
newVariable <- factor(drawtrain$SeriousDlqin2yrs, levels=c(0,1), labels=c("No", "Yes"))
newVariable<-as.data.frame(newVariable)
newdata<-cbind.data.frame(newVariable, as.data.frame(train$age))

```

Information on the competition can be found [here](https://www.kaggle.com/c/GiveMeSomeCredit/data).



# Collaboration

Please indicate who you collaborated with on this assignment: 



# Build binary classifier

Build the binary classifier based on a single predictor variable: `DebtRatio`,
`age`, or `MonthlyIncome`. Justify this choice.


Here I choose to base my predictions of having experienced Deliquency in the last 2 years on age. There is a clear enough difference in the median age between having experience deliquency or not in the  boxplot below. This difference is important for the use of age as a predictor for experiencing deliquency because having a clear age difference between those who experienced deliquency or not is important for establishing a threshold for prediction.


```{r}
ggplot(data=train, aes(x=age))+ labs(x="Age")+ geom_histogram(binwidth = 6)+ggtitle("Distribution of Age")
ggplot(data=newVariable, aes(x=newVariable))+ labs(x="Experienced delinquency?")+ geom_bar()+ggtitle("Distribution of having experienced delinquency in the last 2 years")
ggplot(data=newdata, aes(x=newVariable, y=train$age))+geom_boxplot()+labs(x="Experienced delinquency?", y="Age")+ggtitle("Distribution of age given having experienced delinquency")

```



# ROC curve

Based on the ultimate classifier you choose, plot a corresponding ROC curve.

```{r}
model_formula <- as.formula(train$SeriousDlqin2yrs~train$age)
model_logistic <- glm(model_formula, data=train, family="binomial")

fitted_model <- model_logistic %>% 
  broom::augment() %>% 
  as_tibble() %>% 
  mutate(p_hat = 1/(1 + exp(-.fitted)))
#create empty vector and bind to test set to set set size equal to train set.
X<-as.data.frame(vector(mode = "double",length = 48497))
colnames(X)<-"test$age"
testage<-rbind(as.data.frame(test$age),X)
#make predictions
predictions <- model_logistic %>% 
  broom::augment(newdata=as.data.frame(testage)) %>% 
  mutate(p_hat = 1/(1 + exp(-.fitted)))
#retain only the predictions for the orginal test set
predictions<-predictions[-c(101504:150000),]

```
```{r}

# This bit of code computes the ROC curve
pred <- prediction(predictions = fitted_model$p_hat, labels = fitted_model$train.SeriousDlqin2yrs)
perf <- performance(pred, "tpr","fpr")
# This bit of code computes the Area Under the Curve
auc <- as.numeric(performance(pred,"auc")@y.values)
auc
plot(perf, main=paste("Area Under the Curve =", round(auc, 3)))
```



# ROC curve for random guessing

Instead of using any predictor information as you did above, switch your
predictions to random guesses and plot the resulting ROC curve.

```{r}
flip<-sample(c(0,1),101503,replace=TRUE)
fphat<-sample(0.5, 101503, replace = TRUE)

# This bit of code computes the ROC curve
pred1 <- prediction(predictions = fphat, labels = flip)
perf1 <- performance(pred1, "tpr","fpr")
# This bit of code computes the Area Under the Curve
auc1 <- as.numeric(performance(pred1,"auc")@y.values)
auc1
plot(perf1, main=paste("Area Under the Curve =", round(auc1, 3)))

```
```{r}
#submission file
submit<-submission[,-2] %>% 
  mutate(Probability=predictions$p_hat)
write.csv(submit,file="submission.csv",row.names=FALSE)
```

